\bf A Hierarchical Bayesian Approach for Modeling Infant-Mortality and Wearout Failure Modes

### 2017-07-18 paper/paper.tex
Small edit to abstract.

\bigskip
\begin{abstract}
% Consumers have an interest in accurate assessment of product reliability.  However, lifetime data is often sparse and has limited information.  
While reliability is an important aspect of product quality, by its nature, the lifetime data available to consumers tends to be limited; high-reliability consumer products fail infrequently. Due in part to multiple causes of failure, simple parametric models have limited application, being unable to capture relevant lifetime characteristics. On the other hand, more suitable models are difficult to fit because of small sample sizes. If it were available, failure analysis could mitigate identifiability issues; however, consumers do not have this information, nor is it have practical value for them.

>>>>

\bigskip
\begin{abstract}
% Consumers have an interest in accurate assessment of product reliability.  However, lifetime data is often sparse and has limited information.  
While reliability is an important aspect of product quality, by its nature, the lifetime data available to consumers tends to be limited; high-reliability consumer products fail infrequently. Due in part to multiple causes of failure, simple parametric models have limited application, being unable to capture relevant lifetime characteristics. On the other hand, more suitable models are difficult to fit because of small sample sizes. If it were available, failure analysis could mitigate identifiability issues; however, consumers do not have this information, nor does it have practical value for them.
